\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-10 metatheory-condensed.tex
small edits

\item
\TT also features a set of \emph{linkage transformers} that enable inductive
construction of families: a linkage can be constructed by inheriting or
overriding components of an existing linkage, or by extending an existing
linkage with new components.

>>>>

\item
\TT also features \emph{linkage transformers} modeling the inductive
construction of families from other families.
They allow a linkage to be created by inheriting or
overriding components of an existing linkage, or by extending an existing
linkage with new components.
